---
title: "Assigment - kNN DIY"
author:
  - name author here - Kelvin Wardenaar
  - name reviewer here - Lucie Pinterová
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
   html_notebook:
    toc: true
    toc_depth: 2
---

# Setup - Packages

```{r}
library(tidyverse)
library(googlesheets4)
library(class)
library(caret)
```

# Load Data

```{r}
url <- "https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/data-mining-s2y2122-KelvinWardenaar/master/datasets/KNN-occupancy.csv"
rawDF <- read_csv(url)
```

# Basic Information About Dataset

```{r}
str(rawDF)
```

# Removing Data That Isn't Relevent
##changed -2 to -1 (because dates are not relevant)

```{r}
cleanDF <- rawDF[-1]
head(cleanDF)
```

# Generate The Outcomes We Would Like To Predict

```{r}
cntDiag <- table(cleanDF$Occupancy)
propDiag <- round(prop.table(cntDiag) * 100 , digits = 1)

cntDiag
```

# Converting Them To Percentages

```{r}
propDiag
```

#
##fixed error in releval.factor -> "yes" doesnt exist
```{r}
cleanDF$Occupancy <- factor(cleanDF$Occupancy, levels = c("1", "0"), labels = c("Yes", "No")) %>% relevel("No")
head(cleanDF, 10)
```

# Summerize The Data

```{r}
summary(cleanDF)
```

# Creating a Normalize Funtion and Creating Testsets

```{r}
normalize <- function(x) { # Function takes in a vector
  return ((x - min(x)) / (max(x) - min(x))) # distance of item value - minimum vector value divided by the range of all vector values
}

testSet1 <- c(1:5)
testSet2 <- c(1:5) * 10

cat("testSet1:", testSet1, "\n")
cat("testSet2:", testSet2, "\n")
```

# Using The Normalize Function On Testsets

```{r}
cat("Normalized testSet1:", normalize(testSet1), "\n")
cat("Normalized testSet2:", normalize(testSet1), "\n")
```

# Creating Vectors
## Removed the occupancy

```{r}
nCols <- dim(cleanDF)[2]
cleanDF_n <- sapply(1:(nCols-1),
                    function(x) {
  normalize(cleanDF[,x])
}) %>% as.data.frame()

summary(cleanDF_n)
```

# Creating Feats

```{r}
trainDF_feat <- cleanDF_n[1:5000,  ]
testDF_feat <- cleanDF_n[5001:8143,  ]
```

# Creating Labels

```{r}
trainDF_labels <- cleanDF[1:5000,  6]
testDF_labels <- cleanDF[5001:8143,  6]
```

# Running KNN

```{r}
cleanDF_test_pred <- knn(train = as.matrix(trainDF_feat), test = as.matrix(testDF_feat), cl = as.matrix(trainDF_labels), k = 31)
head(cleanDF_test_pred)
```

# Visualizing It With a Confusion Matrix

```{r}
confusionMatrix(cleanDF_test_pred, testDF_labels[[1]], positive = NULL, dnn = c("Prediction", "True"))
```

---

#Answers

# Setup - Packages
```{r}
library(tidyverse)
library(googlesheets4)
library(class)
library(caret)
```

# Load Data

```{r}
url <- "https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/data-mining-s2y2122-KelvinWardenaar/master/datasets/KNN-occupancy.csv"
```

```{r}
rawDF <- read_csv(url)
```

```{r}
str(rawDF)
```

```{r}
cleanDF <- rawDF[-1]
head(cleanDF)
```

```{r}
cntDiag <- table(cleanDF$Occupancy)
propDiag <- round(prop.table(cntDiag) * 100 , digits = 1)

cntDiag
```

```{r}
propDiag
```

```{r}
cleanDF$Occupancy <- factor(cleanDF$Occupancy, levels = c("1", "0"), labels = c("Yes", "No")) %>% relevel("No")
head(cleanDF, 10)
```

```{r}
summary(cleanDF)
```

```{r}
normalize <- function(x) { # Function takes in a vector
  return ((x - min(x)) / (max(x) - min(x))) # distance of item value - minimum vector value divided by the range of all vector values
}

testSet1 <- c(1:5)
testSet2 <- c(1:5) * 10

cat("testSet1:", testSet1, "\n")
cat("testSet2:", testSet2, "\n")
```

```{r}
cat("Normalized testSet1:", normalize(testSet1), "\n")
cat("Normalized testSet2:", normalize(testSet1), "\n")
```

```{r}
nCols <- dim(cleanDF)[2]
cleanDF_n <- sapply(1:(nCols-1),
                    function(x) {
  normalize(cleanDF[,x])
}) %>% as.data.frame()

summary(cleanDF_n)
```

```{r}
trainDF_feat <- cleanDF_n[1:5000,  ]
testDF_feat <- cleanDF_n[5001:8143,  ]
```


```{r}
trainDF_labels <- cleanDF[1:5000,  6]
testDF_labels <- cleanDF[5001:8143,  6]
```

```{r}
cleanDF_test_pred <- knn(train = as.matrix(trainDF_feat), test = as.matrix(testDF_feat), cl = as.matrix(trainDF_labels), k = 31)
head(cleanDF_test_pred)
```

```{r}
confusionMatrix(cleanDF_test_pred, testDF_labels[[1]], positive = NULL, dnn = c("Prediction", "True"))
```


Choose a suitable dataset from [this](https://github.com/HAN-M3DM-Data-Mining/assignments/tree/master/datasets) folder and train  your own kNN model. Follow all the steps from the CRISP-DM model.


## Business Understanding
text and code here

## Data Understanding
text and code here

## Data Preparation
text and code here

## Modeling
text and code here

## Evaluation and Deployment
text and code here

reviewer adds suggestions for improving the model
