---
title: "Assigment - Naive Bayes DIY"
author:
  - name author here - Lucie Pinterová
  - name reviewer here - Kelvin Wardenaar
date: 13/3/2022
output:
   html_notebook:
    toc: true
    toc_depth: 2
---

```{r}
library(tidyverse)
library(tm)
library(caret)
library(wordcloud)
library(e1071)
```
---


## Business Understanding

The main goal is to make a hate speech detection model by using a Naive Bayes classifier.

The Naive Bayes is a classification algorithm that is suitable for binary and multiclass classification. (Patel, 2021)

It is useful for making predictions and forecasting data based on historical results. (Patel, 2021)

## Data Understanding

The data we will be using comes from private github classroom - the orginal source is not specified.

It contains a set of news (title, author,text) that are labeled with 0 and 1 (fake /true)

```{r}
url <- "https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/data-mining-s2y2122-pinteroval/master/datasets/NB-fakenews.csv"
rawDF <- read_csv(url)
View(rawDF)
```

#Exploring and describing data
```{r}

str(rawDF)
head(rawDF)

```
-> The dataset has 5 variables (columns) and 5572 observations (rows).

-> Columns types:

  ..   id = col_double(),
  ..   title = col_character(),
  ..   author = col_character(),
  ..   text = col_character(),
  ..   label = col_double()

```{r}
rawDF$label <- rawDF$label %>% factor %>% relevel("0")
class(rawDF$label)
```


## Data Preparation

#Shrinking the dataset (because it is too big for easy processing)
```{r}
rawDF <- rawDF [-c(6000:20800),]
```


# Creating a corpus, which refers to a collection of text documents by using the corpus () function

```{r}
rawCorpus <- Corpus(VectorSource(rawDF$text))
inspect(rawCorpus[1:3])
```


# Cleaning of the corpus (everything to lowercase, removing numbers)
```{r}
cleanCorpus <- rawCorpus %>% tm_map(tolower) %>% tm_map(removeNumbers)
```

#Removing items that are not useful for the model (but, and, punctation...)
```{r}
cleanCorpus <- cleanCorpus %>% tm_map(tolower) %>% tm_map(removeWords, stopwords()) %>% tm_map(removePunctuation)
```

#Removing additional whitespace
```{r}
cleanCorpus <- cleanCorpus %>% tm_map(stripWhitespace)
```

# Inspecting the corpus by romparing it to the raw version
```{r}
tibble(Raw = rawCorpus$content[1:3], Clean = cleanCorpus$content[1:3])
```
# Transforming the messages to a matrix
```{r}
cleanDTM <- cleanCorpus %>% DocumentTermMatrix
inspect(cleanDTM)
```

# Split dataset to train and test sets (70%, 30%)
```{r}
# Create split indices
set.seed(1234)
trainIndex <- createDataPartition(rawDF$label, p = .70, 
                                  list = FALSE, 
                                  times = 1)
head(trainIndex)
```
```{r}
# Apply split indices to DF
trainDF <- rawDF[trainIndex, ]
testDF <- rawDF[-trainIndex, ]

# Apply split indices to Corpus
trainCorpus <- cleanCorpus[trainIndex]
testCorpus <- cleanCorpus[-trainIndex]

# Apply split indices to DTM
trainDTM <- cleanDTM[trainIndex, ]
testDTM <- cleanDTM[-trainIndex, ]
```

#Eliminate words with low frequencies
```{r}
freqWords <- trainDTM %>% findFreqTerms(5)
trainDTM <-  DocumentTermMatrix(trainCorpus, list(dictionary = freqWords))
testDTM <-  DocumentTermMatrix(testCorpus, list(dictionary = freqWords))
```

# transform the counts into a factor that  indicates whether the word appears in the document or not
```{r}
# building a function 
convert_counts <- function(x) {
  x <- ifelse(x > 0, 1, 0) %>% factor(levels = c(0,1), labels = c("No", "Yes"))
}
# applying it to columns
nColsDTM <- dim(trainDTM)[2]
trainDTM <- apply(trainDTM, MARGIN = 2, convert_counts)
testDTM <- apply(testDTM, MARGIN = 2, convert_counts)

head(trainDTM[,1:10])
```

## Modeling and Evaluation

```{r}
#using the naiveBayes() function to take in the features and labels of our training dataset and returns a trained model

nbayesModel <-  naiveBayes(trainDTM, trainDF$label, laplace = 1)
```


```{r}
#generating a vector of predictions
predFakeN <- predict(nbayesModel, testDTM)

#using a confusion matrix to analyze the performance of the model
confusionMatrix(predFakeN, testDF$label, positive = "1", dnn = c("Prediction", "True"))
